---
title: "Untitled"
author: "Fred Jaya"
date: '2024-01-18'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(PoolTestR)
library(dplyr)
devtools::load_all("~/GitHub/PoolPoweR/")
```

## Analyse (PoolTestR)

The different Analyse modes are:  
1. Whole data set (PoolPrev)  
2. Stratified (PoolPrev)
3. Whole Prev + Bayesian
4. Strat Prev + Bayesian  
5. Hierarchical (HierPoolPrev)
6. Hierarchical + stratified  

```{r}
simple <- SimpleExampleData

# Arguments shared across all functions
req_args <- list(
  data = simple, # data(),
  result = "Result", # input$colTestResults,
  poolSize = "NumInPool" # input$colUnitNumber
)
```

### 1. Whole data set (PoolPrev)  
```{r}
# stratify_vars = NULL
args <- req_args
args$bayesian <- FALSE

PrevWholeDataset <- do.call(PoolTestR::PoolPrev, args)
PrevWholeDataset
# TODO: Rounding, Rename MLE columns, Remove ProbAbsent, Output 1/1000
```

### 2. Stratified (PoolPrev)
```{r}
stratify_vars <- c("Region", "Year")
args <- c(req_args, lapply(stratify_vars, as.name))
args$bayesian <- FALSE

PrevStrat <- do.call(PoolTestR::PoolPrev, args)
PrevStrat

# write.csv(PrevStrat, "prev_out.csv", row.names = F)
```

### 3. Stratified + Bayes 
```{r}
stratify_vars <- c("Region", "Year")
args <- c(req_args, lapply(stratify_vars, as.name))
args$bayesian <- TRUE

PrevStratBayes <- do.call(PoolTestR::PoolPrev, args)
PrevStratBayes
# TODO: Rounding, Rename MLE columns, Remove ProbAbsent, Output 1/1000
```

### 3. Stratified with bayesian

```{r}
stratify_vars <- c("Region", "Year")
args <- c(req_args, lapply(stratify_vars, as.name))
args$bayesian <- TRUE

PrevRegionYearB <- do.call(PoolTestR::PoolPrev, args)
PrevRegionYearB
# TODO: Rounding, Rename MLE and Bayes columns, Remove ProbAbsent, Output 1/1000,
```

### 4. HierPoolPrev
```{r}
hier_vars <- c("Village", "Site")
args <- req_args
args$hierarchy <- hier_vars

PrevHier <- do.call(PoolTestR::HierPoolPrev, args)
PrevHier
# PrevByHier %>% mutate(across(is.double, round, digits = 4))
# TODO: Rounding, Rename Bayes columns, Remove ProbAbsent, Output 1/1000
```

### 5. HierPoolPrev stratified
```{r}
hier_vars <- c("Village", "Site")
args <- c(req_args, lapply(stratify_vars, as.name))
args$hierarchy <- hier_vars

PrevHierStrat <- do.call(PoolTestR::HierPoolPrev, args)
PrevHierStrat
# PrevHierStrat %>% mutate(across(is.double, round, digits = 4))
# TODO: Rounding, Rename Bayes columns, Remove ProbAbsent, Output 1/1000
```

## Analyse post-processing  

```{r}
PrevStrat_formatted <-
  PrevStrat %>%
  rename(
    "Prevalence (Maximum Likelihood Estimate)" = PrevMLE,
    "Lower Confidence Interval (95%)" = CILow,
    "Upper Confidence Interval (95%)" = CIHigh,
    "Number of Pools" = NumberOfPools,
    "Number of Positive Pools" = NumberPositive
  )

# Functions
prev_per_val_mle <- function(df, val) {
  df %>%
    dplyr::mutate(
      across(
        c(
          `Prevalence (Maximum Likelihood Estimate)`,
          `Lower Confidence Interval (95%)`,
          `Upper Confidence Interval (95%)`
        ),
        ~ . / val
      )
    )
}

rename_perval <- function(df, val) {
  df %>%
    across()

  rename(
    `Prevalence (Maximum Likelihood Estimate)` = PrevMLE,
    `Lower Confidence Interval (95%)` = CILow,
    `Upper Confidence Interval (95%)` = CIHigh
  )
}


rename_perval_bayes <- function(df) {
  df %>%
    rename(
      `Prevalence (Bayesian)` = PrevBayes,
      `Lower Credible Interval (95%)` = CrILow,
      `Upper Credible Interval (95%)` = CrIHigh
    )
}
```

```{r}
prev_per_val_mle(PrevStrat_formatted, 1000)
```

---

## PoolPoweR

```{r}
x <- optimise_sN_prevalence(
  prevalence = 0.005,
  correlation = 0.1,
  cost_unit = 5,
  cost_pool = 10,
  cost_cluster = 20,
  max_N = 20,
  max_s = 50,
  sensitivity = 1,
  specificity = 1,
  form = "logitnorm"
)

y <- as.data.frame(x) %>%
  rename(`Optimal pool size` = s, `Cost` = cost, `Catch` = catch, `Optimal number of pools` = N)
y
```



```{r}
x <- optimise_sN_prevalence(
  prevalence = 0.005,
  correlation = NA,
  cost_unit = 5,
  cost_pool = 10,
  cost_cluster = NA,
  max_N = 20,
  max_s = 50,
  sensitivity = 1,
  specificity = 1,
  form = "logitnorm"
)

y <- as.data.frame(x) %>%
  rename(`Optimal pool size` = s, `Cost` = cost, `Catch` = catch, `Optimal number of pools` = N)
y
```

```{r}
y %>%
  mutate(Cost = round(Cost, digits = 4))
```

```{r}
optimise_random_prevalence(
  # Survey
  cost_cluster = NA,
  # Cost
  cost_unit,
  cost_pool,
  cost_period,
  # Parameters
  pool_strat_family,
  catch_mean,
  catch_variance,
  prevalence,
  correlation = NA,
  # Advanced
  sensitivity = 1,
  specificity = 1,
  max_period = 10,
  form = "logitnorm",
  verbose = FALSE
)
```

```{r}
o <- optimise_random_prevalence(
  catch_mean = 10,
  catch_variance = 11,
  pool_strat_family = pool_target_number,
  prevalence = 0.01,
  cost_unit = 1,
  cost_pool = 4,
  cost_period = 10,
  cost_cluster = 20,
  correlation = 0.1,
  sensitivity = 1,
  specificity = 1,
  max_period = 10,
  form = "logitnorm",
  verbose = FALSE
)

o %>% unlist()
```
```{r}
p <- optimise_random_prevalence(
  catch_mean = 10,
  catch_variance = 11,
  pool_strat_family = pool_max_size,
  prevalence = 0.01,
  cost_unit = 1,
  cost_pool = 4,
  cost_period = 10,
  cost_cluster = 20,
  correlation = 0.1,
  sensitivity = 1,
  specificity = 1,
  max_period = 10,
  form = "logitnorm",
  verbose = FALSE
)

p
```

```{r}
q <- optimise_random_prevalence(
  catch_mean = 10,
  catch_variance = 25,
  pool_strat_family = pool_target_number,
  prevalence = 0.01,
  cost_unit = 1,
  cost_pool = 2,
  cost_period = 50,
  cost_cluster = NA,
  correlation = NA,
  sensitivity = 1,
  specificity = 1,
  max_period = 10,
  form = "logitnorm",
  verbose = FALSE
)

q$pool_strat_pars$target_number
```

```{r}
is_integer_col(simple, "NumInPool")

is.numeric(simple[["NumInPool"]])
```

### Power calculations

4 functions:  
- `power_pool()`  
- `sample_size_pool()`  
- `power_pool_random()`   
- `sample_size_pool_random()`  

```{r}
PoolPoweR::power_pool
```







